partial: An R Package for Creating Partial Dependence Plots

### 2016-08-11 manuscript/greenwell.tex
minor edit
minor edits

Next, we use MARS to to study the relationship between atmospheric ozone (\code{ozone}) concentration and meteorology in the Los Angeles basin in 1976, allowing for up to three-way interactions.
\begin{example}
ozone.earth <- earth(ozone ~ ., data = ozone, degree = 3)
summary(ozone.earth)
\end{example}
The model produced a generalized $R^2$ of $0.788$, similar to what was reported in \citet{breiman-1985-estimating}. A single three-way interaction was found involving the predictors
\begin{itemize}
  \item \code{wind}: wind speed (mph) at Los Angeles International Airport (LAX)
  \item \code{temp}: temperature ($^oF$) at Sandburg Air Force Base
  \item \code{dpg}: the pressure gradient (mm Hg) from LAX to Dagget, CA
\end{itemize}
To understand this interaction, we can use a partial plot. However, since the partial dependece between three continuous variables can be computationally expensive, we will run \code{partial} in parallel.

>>>>

Next, we use MARS to model ozone concentration as a nonlinear function of the eight meteorological variables plus day of the year; we allow for up to three-way interactions.
\begin{example}
ozone.earth <- earth(ozone ~ ., data = ozone, degree = 3)
summary(ozone.earth)
\end{example}
The model produced a generalized $R^2$ of $0.79$, similar to what was reported in \citet{breiman-1985-estimating}. A single three-way interaction was found involving the predictors
\begin{itemize}
  \item \code{wind}: wind speed (mph) at Los Angeles International Airport (LAX)
  \item \code{temp}: temperature ($^oF$) at Sandburg Air Force Base
  \item \code{dpg}: the pressure gradient (mm Hg) from LAX to Dagget, CA
\end{itemize}
To understand this interaction, we can use a partial plot. However, since the partial dependece between three continuous variables can be computationally expensive, we will run \code{partial} in parallel.
